---
title: "IC Papers Analysis"
author:
  - name: "Emir Turkes [emir.turkes@eturkes.com]"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile,
    encoding = encoding,
    output_file = file.path("..", "results", "ic-papers-analysis.html")
  )})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
h3 {font-size: 20px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
.tocify-subheader .tocify-subheader .tocify-item {
  font-size: 0.95em; padding-left: 35px; text-indent: 0;
}
div.main-container {max-width: none; width: 100%;}
</style>

*This file is a part of [IC Papers Analysis](https://github.com/eturkes/ic-papers-analysis).*

A quick analysis of research articles that use or discuss Intellicage.

R code used in each section can be expanded with the CODE button at the right.  
Toggling the first CODE button at the start of the document enables showing and hiding of all code.

```{r}
# Load in necessary boilerplate and libraries.
# --------------------------------------------

# Copyright 2020-2023 Emir Turkes
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
#     http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software
# distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and
# limitations under the License.

packages <- c("conflicted", "bib2df", "dplyr", "ggplot2", "DT", "scales", "pals")
invisible(suppressPackageStartupMessages(lapply(packages, library, character.only = TRUE)))
conflict_prefer("filter", "dplyr", quiet = TRUE)
source("utils.R")

knitr::opts_chunk$set(dpi = 300)
# --------------------------------------------
```

# Raw Data

```{r}
data <- suppressWarnings(bib2df(file.path("..", "ic-papers.bib")))
data <- data[-which(data$YEAR == "2023"), ] # Only include years that have fully passed.

datatable_download(data[ , c(5, 13, 23, 26, 29)])

categories <- read.csv(file.path("..", "assets", "paper-categories.csv"), row.names = 1)

datatable_download(categories)

categories <- lapply(split(categories, row.names(categories)), unlist)
categories <- lapply(categories, function(x) x[!(x == "")])

categories_df <- data.frame(Category = names(categories))
categories_df$`Number of Papers` <- unlist(lapply(categories, length))

categories_df <- categories_df %>%
  mutate(Proportion = `Number of Papers` / sum(`Number of Papers`)) %>%
  arrange(Proportion) %>%
  mutate(Percentage = percent(Proportion))

categories_df <- categories_df[order(categories_df$`Number of Papers`, decreasing = TRUE), ]
rownames(categories_df) <- NULL

datatable_download(categories_df)
```

# Figures

## Publications Per Year

```{r}
ggplot(data, aes(YEAR)) +
  stat_count(geom = "line", aes(y = ..count..), size = 0.5, color = "#0072B2") + 
  stat_count(
    geom = "point", aes(y = ..count..), color = "white", fill = "#0072B2", shape = 21, size = 2
  ) +
  scale_x_continuous(n.breaks = length(unique(data$YEAR))) +
  scale_y_continuous(n.breaks = length(unique(data$YEAR))) +
  labs(x = "Year", y = "Number of Publications") +
  theme_classic() +
  theme(panel.grid.major = element_line(colour = "grey92")) +
  ggtitle("Number of Intellicage Publications in Each Year")
```

## Publications Over Time (Cumulative)

```{r}
ggplot(data, aes(YEAR)) +
  stat_count(geom = "line", aes(y = cumsum(..count..)), size = 0.5, color = "#0072B2") + 
  stat_count(
    geom = "point", aes(y = cumsum(..count..)), color = "white", fill = "#0072B2", shape = 21, size = 2
  ) +
  scale_x_continuous(n.breaks = length(unique(data$YEAR))) +
  scale_y_continuous(n.breaks = 15) +
  labs(x = "Year", y = "Number of Publications") +
  theme_classic() +
  theme(panel.grid.major = element_line(colour = "grey92")) +
  ggtitle("Number of Intellicage Publications Over Time (Cumulative)")
```

## Papers Per Study Area

### Full Pie Chart

```{r}
ggplot(categories_df, aes("", Proportion, fill = Category)) +
  geom_col(color = "black") +
  geom_label(
    aes(label = paste0("Papers: ", `Number of Papers`, " (", Percentage, ")")),
    position = position_stack(vjust = 0.5),
    show.legend = FALSE,
    size = 3
  ) +
  guides(fill = guide_legend(title = "Category")) +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = cols25(nrow(categories_df))) +
  ggtitle("Papers Per Study Area")
```

### Top 5 Categories Pie Chart

```{r}
categories_df_small <- categories_df[1:4, 1:2]
new_row <- data.frame("Other", sum(categories_df$`Number of Papers`[5:18]))
colnames(new_row) <- c("Category", "Number of Papers")
categories_df_small <- rbind(categories_df_small, new_row)

categories_df_small <- categories_df_small %>%
  mutate(Proportion = `Number of Papers` / sum(`Number of Papers`)) %>%
  arrange(Proportion) %>%
  mutate(Percentage = percent(Proportion))

categories_df_small <- categories_df_small[order(categories_df_small$`Number of Papers`, decreasing = TRUE), ]
rownames(categories_df_small) <- NULL

ggplot(categories_df_small, aes("", Proportion, fill = Category)) +
  geom_col(color = "black") +
  geom_label(
    aes(label = paste0(`Number of Papers`, " (", Percentage, ")")), position = position_stack(vjust = 0.5),
    show.legend = FALSE
  ) +
  guides(fill = guide_legend(title = "Category")) +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = cols25(nrow(categories_df_small))) +
  ggtitle("Papers Per Study Area")
```

### Bar Chart

```{r, fig.width = 8}
categories_df$Category <- factor(categories_df$Category, rev(categories_df$Category))
sum <- sum(categories_df$`Number of Papers`)

ggplot(categories_df, aes(Category, `Number of Papers`, fill = Category)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(
    sec.axis = sec_axis(~. / sum * 100, name = "Percentage of Total Papers", breaks = seq(0, 20, 1)),
    breaks = seq(0, 60, 2)
  ) +
  coord_flip() +
  theme_classic() +
  theme(panel.grid.major = element_line(colour = "grey92"), legend.position = "none") +
  geom_col(color = "black") +
  ggtitle("Papers Per Study Area")
```

# References

This is the concluding section of the document.
Here we output the `sessionInfo` and create a bibliography for works cited.

```{r}
sessionInfo()
```
